---
title: "Using widgetframe"
author: "Bhaskar V. Karambelkar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using widgetframe}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The goal of widgetframe is to be able to embed widgets inside iframes using NPR's [Pymjs](http://blog.apps.npr.org/pym.js/) library for responsive iframes.

This package provides two functions `frameableWidget`, and `frameWidget`. The `frameableWidget` is used to add extra code to a htmlwidget which allows is to be rendered inside a responsive iframe. The `frameWidget` returns a htmlwidget which displays content of another htmlwidget inside a responsive iframe. 

### Current Status

- Works With
    * [Flex Dashboard](http://rmarkdown.rstudio.com/flexdashboard/): Check out this [Demo](https://rawgit.com/bhaskarvk/widgetframe/master/inst/examples/flexdashboard/dashboard.html).
    * [RMarkdown](rmarkdown.rstudio.com) + [knitr](yihui.name/knitr/): Check out this [Demo](https://rawgit.com/bhaskarvk/widgetframe/master/inst/examples/rmarkdown/knitr_example.html).
    * [RMarkdown Website](http://rmarkdown.rstudio.com/lesson-13.html): Check out this [Demo](https://rawgit.com/bhaskarvk/widgetframe/master/inst/examples/rmarkdown-website/index.html).
    * [Xaringan Presentations](https://slides.yihui.name/xaringan/): Check out this [Demo](https://rawgit.com/bhaskarvk/widgetframe/master/inst/examples/xaringan/widgetframe.html#1).<br/>(May also work with other RMarkdown + knitr based presentations.)
    * [Bookdown](https://bookdown.org/) gitbook: Needs a Makefile, but works. Check out this [Demo](https://rawgit.com/bhaskarvk/widgetframe/master/inst/examples/bookdown/book/index.html).

<br/>

- Does Not (Yet) Work With
    * Shiny
    * [blogdown](https://github.com/rstudio/blogdown/): See [issue#38](https://github.com/rstudio/blogdown/issues/38)

### Installation

```{r, eval=FALSE}
if(!require(devtools)) {
  install.packages('devtools')
}
devtools::install_github('bhaskarvk/widgetframe')
```

### Usage

#### `frameableWidget` function.

The `frameableWidget` function should be used when you need a HTML which can be embedded in a CMS system like WordPress/blogger or a static HTML website using the [Pymjs](http://blog.apps.npr.org/pym.js/) library.

```{r, eval=FALSE}
library(leaflet)
library(widgetframe)
l <- leaflet() %>% addTiles()
htmlwidgets::saveWidget(frameableWidget(l),'leaflet.html')
```

The resulting leaflet.html contains the necessary Pym.js Child initialization code and will work inside a regular iFrame or better yet a Pym.js responsive iFrame. It is expected that the site which is going to embed this widget's content has the necessary Pymjs Parent initialization code as described [here](http://blog.apps.npr.org/pym.js/).

#### `frameWidget` function

`frameWidget` function takes an existing htmlwidget as an argument and returns a new htmlwidget which when rendered, wraps the input htmlwdiget inside a responsive iFrame. This function can be used to knit htmlwidgets such that they are unaffected by the parent HTML file's CSS. This could be useful in [bookdown](https://bookdown.org/) or [R Markdown Websites](http://rmarkdown.rstudio.com/rmarkdown_websites.html) to embed widgets such that they are unaffected by the site's global CSS/JS.

You can use `widgetFrame` inside your R Markdowns as shown below.

```
```{r}
library(leaflet)
library(widgetframe)
l <- leaflet(height=300) %>% addTiles() %>% setView(0,0,1)
frameWidget(l)
```
```

```
```{r}
library(dygraphs)
ts <- dygraph(nhtemp, main = “New Haven Temperatures”,
              height=250, width=‘95%’) 
frameWidget(ts)
```
```
